Metropolitan Areas (Deaths & Case)

### 2020-11-24 KPMG Team/Dashboard/visualization_scripts/msa_county_state_cities.Rmd
county viz wave 2

county_sum_w2 <- county_sum_total %>% 
  inner_join(county_sum_wave_2_start, by = c("fips", "county")) %>% 
  mutate(cases = cases.x - cases.y) %>%
  mutate(deaths = deaths.x - deaths.y) %>% 
  rename(start_date = date.y) %>% 
  rename(end_date = date.x) %>%
  select(fips, county, population, start_date, end_date, cases, deaths)

@@

@@

@@

library(cowplot)
library(gridExtra) # for grid plot

>>>>

county_sum_w2 <- county_sum_total %>% 
  inner_join(county_sum_wave_2_start, by = c("fips", "county")) %>% 
  mutate(cases = cases.x - cases.y) %>%
  mutate(deaths = deaths.x - deaths.y) %>% 
  rename(start_date = date.y) %>% 
  rename(end_date = date.x) %>%
  select(fips, county, all_of(population), start_date, end_date, cases, deaths)

@@

data_msa$fips

@@

census_msa_merge$fips

@@

# library(cowplot)
library(gridExtra) # for grid plot
